### 2018-12-14 writing/thesis/chapters/results.tex
Add small paragraph about convergence results.

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {L1} & {L2} & {LInf}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.56\\
3 & 3.44 & 3.41 & 3.42\\
4 & 4.27 & 4.27 & 4.33\\
5 & 5.36 & 5.32 & 5.26\\
6 & 5.38 & 5.35 & 5.17\\
\bottomrule
\end{tabular}
\end{table}
\newcommand{\error}{\operatorname{Total-Error}}

@@

>>>>

\chapter{Results}\label{chap:results}
\section{Convergence Test}
\begin{table}[htb]
  \centering
\caption{Numerical order of convergence of ADER-DG method}%
\label{tab:convergence-order}
\begin{tabular}{@{}lS[table-format=1.2]S[table-format=1.2]S[table-format=1.2]@{}}
\toprule
{Order} & {$L_1$} & {$L_2$} & {$L_\infty$}\\ \midrule
1 & 2.03 & 2.00 & 1.92\\
2 & 2.56 & 2.55 & 2.56\\
3 & 3.44 & 3.41 & 3.42\\
4 & 4.27 & 4.27 & 4.33\\
5 & 5.36 & 5.32 & 5.26\\
6 & 5.38 & 5.35 & 5.17\\
\bottomrule
\end{tabular}
\end{table}
\newcommand{\error}{\operatorname{Total-Error}}

@@

We compute the error for the manufactured-solution scenario (\cref{sec:manufactured-solution}).
Looking at the plot for the $L_2$ error (refer to plot here) shows that our method converges for all tested polynomial orders.
\todo{Preliminary results used here!}

To compute the numerical order of convergence, we perform a linear regression of the logarithm of the error vs.\ the logarithm of the meshsize.
The size of the slope is then the convergence order.
We can see (\cref{tab:convergence-order}) that our numerical convergence rate increases with the polynomial order.
We do not achieve the optimal theoretical order of convergence of $N+1$.
In~\cite{dumbser2010arbitrary}, which use a similar numerical method and the same scenario, but a different grid, \citeauthor{dumbser2010arbitrary} achieves the optimal order for most polynomial orders.
Some \textsc{dg}-methods of odd order only achieve a numerical convergence order of $N+\nicefrac{1}{2}$.
